---
title: "r proficiency test"
output: html_notebook
---

#before you start, please save this file with the same name and your name concatenated at the end. See full instructions bellow. 


###run the following chunk order to upload the datafiles - see details below
```{r preparing the dataset, include=FALSE,echo=FALSE}
rm(list = ls())

library(Rmisc);library(tidyverse); library(lme4); library(lmerTest); 
library(jsonlite)
path = "data/"
d <-
    list.files(path,pattern="*.json", full.names = T) %>% #get a list of all  files
    map_df(~fromJSON(file.path(.),
              simplifyVector = TRUE, 
              flatten = T)) #add these files to d

d=as.data.frame(d)

d = d%>%
  filter(name =="valence" | name == "rating" | name == "emotionType" )%>%
  select(rt,trial_index,participant_id,stimulus,button_pressed,name,response)%>%
  mutate(photo = ifelse(name=="rating", lag(stimulus), stimulus),
         value = ifelse(is.na(button_pressed),response,button_pressed))%>%
  separate(photo,into = c("folder", "fileEnding"), sep = "\\/")%>%
  separate(fileEnding, into=c("photo","fileEnding"), sep = "\\.")%>%
  select(-stimulus,-button_pressed,-response,-folder,-fileEnding,-rt,-trial_index)%>%
  group_by(participant_id)%>%
  mutate(trial = rep(1:30,each=3 ))%>%
  ungroup()%>%
  spread(name,value)%>%
  arrange(participant_id,trial)
  
  
  
d$photo = as.integer(d$photo)
d$rating=as.integer(d$rating)

d$valence=factor(d$valence,label= c("positive", "negative","neutral"))




#combind moderator file
m = read_csv('moderators.csv') # we are reading the moderators file (which was collected via qualtrics)
m = m[,c(18:49)] #cleaning


d =m%>% select(participant_id, 
           poli, 
           age, 
           gender, 
           black, 
           latin, 
           white, 
           asian, 
           other)%>%
  left_join(d,.) #combining the two datasets based on participants' id

rm(m)

```

The goal of this task was to pilot participants' responses to a series of pictures. in response to each pictures particiapnts were asked to answer a few questions. the database d contains that following columns:

1. participant_id
2. photo - an emotional photo that participants saw.
3. trial - trial number.
4. emotionType - participants chose from a list of emotions :  "Happiness", "Excitment", "Calmness", "Sadness","Anger","Guilt", "Fear","Hatred"
5. participants ratings of intensity in response to the picture.
6. valence - whehther participants rated the pictures as positive negative or neutral.
7. poli - participants' political affiliation from 1- extreme liberals to 7 - extreme conservatives.
8. age 
9. gender - 1 woman, 2 men, 3 other. 
10-14: black, latin, white, asian, other - participatns were asked to mark their race. 


#descriptives - answer the following questions with code
```{r}

# how many participants particiapted in the study.


#how many photoes were there in the study, how many were observed by each participants. 


#create a historgram of participants' political affiliation


#create a table with participants' race. 


```


# in the chunk below - for each photo: what was the precent of positive and negative emotions. Provide both a table and a graph.
```{r photoes data}


```


#provide frequency graph for the different types of emotions: "photo", "Happiness", "Excitment", "Calmness", "Sadness","Anger","Guilt", "Fear","Hatred"

```{r distinct emotions}


```


#crate a graph for each photo and its average rating (with confidence intervals)
```{r}


```


#is rating predicted by emotion? Use lmer for the analysis if possibile

```{r}

```

